Influence of Connectivity on Dung Beetle Communities

### 2025-06-20 corridor_docs/eric_ms_thesis/MS_thesis.Rmd
formatting

header-includes:
  - \AtBeginDocument{\let\maketitle\relax} # this removes default title section
  - \usepackage{float} #to keep figure in the location placed instead of end
  - \floatplacement{figure}{H}
  - \usepackage{booktabs}
  - \raggedbottom
  - \usepackage{fancyhdr}
  - \pagestyle{plain}
  - \fancyfoot[C]{\thepage}
  - \fancyhead[L]{}
  - \fancyhead[R]{\small{EEC MS Thesis Draft}}
  - \thispagestyle{fancy}
  - \usepackage{tabu}
  - \usepackage{makecell}
  - \usepackage{pdflscape}
  - \usepackage{longtable}
  - \newcommand{\blandscape}{\begin{landscape}}
  - \newcommand{\elandscape}{\end{landscape}}
  - \setlength\parindent{22pt}
  - \usepackage{indentfirst}
  - \renewenvironment{abstract}{}{} #suppress the abstract
  - \usepackage{setspace}

@@

\vspace{8cm}

@@

\vspace{6cm}

@@

\vspace{3cm}

@@

\begin{center}
A THESIS PRESENTED TO THE GRADUATE SCHOOL OF THE UNIVERSITY OF FLORIDA IN PARTIAL FULFILLMENT OF THE REQUIREMENTS FOR THE DEGREE OF MASTER OF SCIENCE
\end{center}

\vspace{2cm}

@@

\vspace{20cm}

@@

\vspace{15cm} 
<!-- _Your dedication is typed here. It should begin with the word “To.” (To my Mom is a typical dedication) If your dedication is longer than a single line it should be single-spaced, and centered vertically and horizontally_ -->

@@

ACKNOWLEDGMENTS

\end{center}
<!-- _Acknowledgments must be written in complete sentences. Do not use direct address. For example, instead of Thanks, Mom and Dad!, you should say I thank my parents._  -->
\begin{center}

@@

\end{center}

@@

LIST OF ABBREVIATIONS

\end{center}

@@

Abstract of Thesis Presented to the Graduate School

of the University of Florida in Partial Fulfillment of the

Requirements for the Degree of Master of Science.

\end{center}

THE INFLUENCE OF CONNECTIVITY ON DUNG BEETLE COMMUNITIES

By

Eric Escobar-Chena

August 2025

Chair: Emilio Bruna 
Major: Wildlife Ecology and Conservation

@@

@@

**CHAPTER 1**

**Influence of Connectivity on Dung Beetle Communities**

@@

# BIOGRAPHICAL SKETCH

>>>>

header-includes:
  - \AtBeginDocument{\let\maketitle\relax} # this removes default title section
  - \usepackage{float} #to keep figure in the location placed instead of end
  - \floatplacement{figure}{H}
  - \usepackage{booktabs}
  - \raggedbottom
  - \usepackage{fancyhdr}
  - \pagestyle{plain}
  - \fancyfoot[C]{\thepage}
  - \fancyhead[L]{}
  - \fancyhead[R]{\small{EEC MS Thesis Draft}}
  - \thispagestyle{fancy}
  - \usepackage{tabu}
  - \usepackage{makecell}
  - \usepackage{pdflscape}
  - \usepackage{longtable}
  - \newcommand{\blandscape}{\begin{landscape}}
  - \newcommand{\elandscape}{\end{landscape}}
  - \setlength\parindent{22pt}
  - \usepackage{indentfirst}
  - \renewenvironment{abstract}{}{} #suppress the abstract
  - \usepackage{setspace}
  - \setcounter{secnumdepth}{0} # removes numbering from sections and subsections
  - \usepackage{sectsty}\allsectionsfont{\raggedright}
  - \usepackage{sectsty}\sectionfont{\centering}{\normalfont} # center # headings
  - \usepackage{sectsty}\subsectionfont{\centering}{\normalfont} # center ## headings
  - \usepackage{sectsty}\subsubsectionfont{\normalfont} # center ## headings
  # - \usepackage{sectsty}\subsubsectionfont{\itshape} # no centering but italic subsu
  # - \usepackage{sectsty}\subsubsectionfont{\centering}{ital} # center ### headings
  # - \usepackage{sectsty}\sectionfont{\centering\color{darkmidnightblue}}

@@

\vspace*{5cm}

@@

@@

\vspace{1cm}

@@

\begin{center}
A THESIS PRESENTED TO THE GRADUATE SCHOOL\\  
OF THE UNIVERSITY OF FLORIDA IN PARTIAL FULFILLMENT\\ 
OF THE REQUIREMENTS FOR THE DEGREE OF\\  
MASTER OF SCIENCE\\
\end{center}

\begin{center}
UNIVERSITY OF FLORIDA
\end{center}

@@

\vspace*{11cm}

@@

\vspace*{10cm} 
<!-- _Your dedication is typed here. It should begin with the word “To.” (To my Mom is a typical dedication) If your dedication is longer than a single line it should be single-spaced, and centered vertically and horizontally_ -->

@@

\textbf{ACKNOWLEDGMENTS}

\end{center}
<!-- _Acknowledgments must be written in complete sentences. Do not use direct address. For example, instead of Thanks, Mom and Dad!, you should say I thank my parents._  -->
\doublespacing

@@

@@

\begin{center}  
\textbf{LIST OF ABBREVIATIONS}
\end{center}

\vspace{1cm}

@@

\vspace*{5cm}

\singlespacing

\begin{center}  
Abstract of Thesis Presented to the Graduate School\\  
of the University of Florida in Partial Fulfillment of the\\  
Requirements for the Degree of Master of Science.\\   
\end{center}

\vspace*{1cm}

\begin{center}
Eric Escobar-Chena   
\end{center}

\begin{center}
August 2025   
\end{center}

\begin{flushleft}
Chair: Emilio Bruna\\  
Major: Wildlife Ecology and Conservation\\   
\end{flushleft}

@@

\begin{center}
CHAPTER 1\\  
INFLUENCE OF CONNECTIVITY ON DUNG BEETLE COMMUNITIES\\  
\end{center}

@@

@@

\vspace*{1cm}

\begin{center}
\textbf{BIOGRAPHICAL SKETCH}
\end{center}
